Lightness constancy under fixed geometry

### 2017-10-10 Draft1/draft1.tex
restrucuturing
editing

In this work, we study a simpler analogue of color constancy called lightness constancy. Here, we consider the lightness component of the 3D color space. Lightness is the attribute that determines the brightness of a color. For achromatic objects, it is the property that changes from black to gray to white. A color with a low lightness is nearly black, while one with a high lightness is the pure, saturated color. We study the effects of variations in the reflected light on the perceived lightness of an object.

% Figure 1: Introduction
\begin{figure}[h]
\centering
\begin{subfigure}{0.4 \textwidth}
		\centering
        \includegraphics[width=\textwidth]{Figures/Figure1/Figure1_a.png}
        \caption{}
        \label{fig:introSchematic}
    \end{subfigure}
    \begin{subfigure}{0.45 \textwidth}   
        \includegraphics[width=\textwidth]{Figures/Figure1/Figure1_b.jpeg}
        \caption{}
        \label{fig:introExampleFigure}
    \end{subfigure}
    \label{introFigure}
    \caption{(a) {\bf Color Constancy:} The light reflected off an object and incident on our eyes, depends both on the surface reflectance of the object $\left( R(\lambda,x) \right)$ and the illumination spectrum of the light source $\left(E(\lambda,x)\right)$. Additionally, the reflected light also depends on context the object lies in. Thus a variation in the reflected light can result from either a change in the object surface reflectance, or a change in the illumination spectrum of the light source, or change in the context, or all of these. Color constancy refers to the ability of the human visual system to perceive the color of the object stably under variations coming from these factors. (b) {\bf Lightness Constancy Under Spectral Variations:} In this work we study lightness constancy under variations in the spectra of the light sources and the objects. In Fig.\ref{fig:introExampleFigure}, we show 5 images generated at three different lightness levels of the target object (spherical object in the center). Along the rows we have fixed the lightness level of the target object, while we vary the spectra of the target object, the background objects and the light sources. (For illustration, in fig.\ref{fig:introExampleFigure}, We have fixed the shape of the target object reflectance spectra along the column.) Our aim is to identify computations that can recover the target object lightness from such stimuli.} 
\end{figure}

The factors that lead to variations in the reflected light can broadly be categorized into two categories: geometrical (shape,size, relative position, etc.) and spectral (surface reflectance, diffusivity, etc.). Here we focus on spectral variations. Specifically, we study the effects of variations in the surface reflectance spectra and the illumination spectra on lightness. We are interested in identifying the computations that should be performed on the visual signal to achieve lightness constancy (Fig.\ref{fig:introExampleFigure}).

@@

Our approach involves generating a database of multi-spectral images of naturalistic scenes, labeled by the lightness of a specific target object in the scene. The label refers to the perceived lightness of the target object if it were placed under a standard light source ($D_{65}$ daylight spectrum). We generate hundreds of multi-spectral images at several fixed values of the target object standard lightness. At a particular lightness level, we allow variations in the surface reflectance spectra of the objects (both the target and surround) and the illumination spectra of the light sources (Fig. \ref{fig:introExampleFigure}. Here we show the results for three cases resulting from the combination of such spectral variations (Fig.\ref{fig:studiedCases}. These are: 1. Variations in target object spectra (Fig.\ref{fig:targetVarying}) with fixed illumination and background surface reflectance spectra, 2. Variations in target object spectra and the light source spectra, with fixed background surface reflectance spectra (Fig.\ref{fig:targetIlluminantVarying}), and 3. Variations in all spectra (target object, background object and light source) (Fig.\ref{fig:allSpectraVarying}). The effects of other types of spectral variations can be explained in terms of one of these cases (see supplementary information).

% Figure 2: Cases Studied
\begin{figure}
\centering
	\begin{subfigure}[b]{0.33 \textwidth}
		\includegraphics[width=\textwidth]{Figures/Figure2/Figure2_a.jpeg}
		\caption{Case 1}
 		\label{fig:targetVarying}
	\end{subfigure}
	\begin{subfigure}[b]{0.33 \textwidth}
        \includegraphics[width=\textwidth]{Figures/Figure2/Figure2_b.jpeg}
        \caption{Case 2}
        \label{fig:targetIlluminantVarying}
    \end{subfigure}
	\begin{subfigure}[b]{0.33 \textwidth}
        \includegraphics[width=\textwidth]{Figures/Figure2/Figure2_c.jpeg}
        \caption{Case 3}
        \label{fig:allSpectraVarying}
    \end{subfigure}    
    \caption{{\bf Spectral Variations Studied:} sRGB rendition of images studied in our work. The numbers on the left are the standard lightness level of the target object. We show 5 images for each case at 3 lightness levels. The analysis was performed with images at 10 lightness levels. We studied three types of spectral variations. (a) Case 1: Target reflectance spectra variable, Background reflectance spectra fixed, illuminant spectra fixed (b) Case 2: Target reflectance spectra variable, Background reflectance spectra fixed, illuminant spectra variable (c) Case 3: Target reflectance spectra variable, Background reflectance spectra variable, illuminant spectra variable.}
\label{fig:studiedCases}
\end{figure}

Having generated the database of labeled multi-spectral images for each one of these cases, we simulate the retinal cone response to these images using an accurate model of the front end of the visual system. The cone-responses dataset, labeled with the standard lightness of the target object, are analyzed using supervised computational learning methods. We have employed three supervised computational learning methods for estimating the target object lightness: linear regression, SVD-LDA regression and accuracy maximization analysis. These methods identify the computations that need to be performed on the cone-responses to estimate the target object lightness. Finally, we evaluate the performance of the computational methods on a test set of images.

In the following, we describe each one of these stages of our approach in detail. In the methods section, we first describe the process to generate naturalistic labeled images (\nameref{method:VirtualWorld}). Next, we describe the steps to simulate the response of the visual system to these images (\nameref{method:Isetbio}). Finally, we describe the three learning methods we have used in our analysis (\nameref{method:SupervisedLearning}). In the results section, we first the show the estimates and performance of each one of the supervised methods for the three cases with different spectral variations. We show that for spectral variations that allow variation either only in the shape of the target surface reflectance or the background surface reflectance or the spectral power distribution of the source of light, the standard lightness, $Y_{65}$ can be recovered by simple manipulations of the reflected light captured by the visual system. For example, if the illumination spectra of the light sources and the background are held fixed, wile the target reflectance spectra change (case 1), $Y_{65}$ can be recovered directly from the light reflected off the target object. If  the surface reflectance of the target object  and the illumination spectra of the light sources are allowed to vary, with fixed background reflectance spectra (case 2), $Y_{65}$ can be recovered by from the contrast between the target and the background. When all the spectral features in the scene are allowed to change (case 3), $Y_{65}$ can not be recovered from a simple manipulations of the light captured by the visual system. Here, we have used a Bayesian supervised learning method called accuracy maximization analysis to estimate $Y_{65}$ of the target object. Using this method, we can recover the lightness of the target object with $\sim 15\%$ relative root mean square error.

@@

% Figure 3: Methods
\begin{figure}
\centering
\begin{subfigure}[b]{0.25 \textwidth}
		\centering
        \includegraphics[width=\textwidth]{Figures/Figure3/Figure3_a.png}
        \caption{A typical 3D Scene}
        \label{fig:3DScene}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.19 \textwidth}   
    \hspace{0.1 \textwidth}
        \includegraphics[width=\textwidth]{Figures/Figure3/Figure3_b.png}
        \caption{Cropped Image}
        \label{fig:croppedImage}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.19 \textwidth}
    \hspace{0.1 \textwidth}
        \includegraphics[width=\textwidth]{Figures/Figure3/Figure3_c.png}
        \caption{Optical Image}
        \label{fig:croppedImageWithMosaic}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.2 \textwidth}
        \includegraphics[width=\textwidth]{Figures/Figure3/Figure3_d.png}
        \caption{LMS cone contrast}
        \label{fig:coneContrast}
    \end{subfigure}

@@

% Figure 4
\begin{figure}
\centering
\begin{subfigure}[b]{0.27 \textwidth}
		\centering
        \includegraphics[width=\textwidth]{Figures/Figure4/Figure4_a.pdf}
        \caption{SVD First 2 RFs}
        \label{fig:case9SVD}
    \end{subfigure}
    \begin{subfigure}[b]{0.27 \textwidth}   
        \includegraphics[width=\textwidth]{Figures/Figure4/Figure4_b.pdf}
        \caption{AMA First 2 RFs}
        \label{fig:case9AMA}
    \end{subfigure}
        \begin{subfigure}[b]{0.20 \textwidth}
        \includegraphics[width=\textwidth]{Figures/Figure4/Figure4_c.pdf}
        \caption{AMA RF Response}
        \label{fig:case9FiltersResponse}
    \end{subfigure}
        \begin{subfigure}[b]{0.20 \textwidth}
        \includegraphics[width=\textwidth]{Figures/Figure4/Figure4_d.pdf}
        \caption{Lightness Estimates}
        \label{fig:case9Results}
    \end{subfigure}    
    \caption{{\bf Receptive fields and lightness estimates. Case 1:} (a) First two receptive fields produced by the SVD method. Along the row we show the filters corresponding to the L cones, M cones and Scones (left to right). (c) First two receptive fields produced by the SVD method. (c) The response of the stimuli to the first two AMA filters. The responses are grouped with the label of the stimuli. As is clear, the response separate out quite well in this case, making the estimation easy (d) The estimates of the target object standard lightness. The naive method produces the mean value of the target luminance used in the analysis. The shaded region corresponds to 1 sigma standard deviation.}
\label{fig:case9AllResults}
\end{figure}

% Figure 5
\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{Figures/Figure5/Figure5.pdf}
\caption{{\bf Performance with number of RFs used for estimation:} Most of the information is captured by the first two filters. We have used the first 8 RFs in our analysis.}
\label{fig:RMSEvsNFilters}
\end{figure}

% Figure 6
\begin{figure}
\centering
\begin{subfigure}[b]{0.27 \textwidth}
		\centering
        \includegraphics[width=\textwidth]{Figures/Figure6/Figure6_a.pdf}
        \caption{SVD First 2 RFs}
        \label{fig:case10SVD}
    \end{subfigure}
    \begin{subfigure}[b]{0.27 \textwidth}   
        \includegraphics[width=\textwidth]{Figures/Figure6/Figure6_b.pdf}
        \caption{AMA First 2 RFs}
        \label{fig:case10AMA}
    \end{subfigure}
        \begin{subfigure}[b]{0.20 \textwidth}
        \includegraphics[width=\textwidth]{Figures/Figure6/Figure6_c.pdf}
        \caption{AMA RF Response}
        \label{fig:case10FiltersResponse}
    \end{subfigure}    
        \begin{subfigure}[b]{0.2 \textwidth}
        \includegraphics[width=\textwidth]{Figures/Figure6/Figure6_d.pdf}
        \caption{Luminance Estimates}
        \label{fig:case10Results}
    \end{subfigure}
    \label{fig:case10AllResults}
    \caption{{\bf Receptive fields and lightness estimates. Case 2:} Same as Fig. \ref{fig:case9AllResults}.}
\end{figure}

% Figure 7
\begin{figure}
\centering
\begin{subfigure}[b]{0.27 \textwidth}
		\centering
        \includegraphics[width=\textwidth]{Figures/Figure7/Figure7_a.pdf}
        \caption{SVD First 2 RFs}
        \label{fig:case12SVD}
    \end{subfigure}
    \begin{subfigure}[b]{0.27 \textwidth}   
        \includegraphics[width=\textwidth]{Figures/Figure7/Figure7_b.pdf}
        \caption{AMA First 2 RFs}
        \label{fig:case12AMA}
    \end{subfigure}
        \begin{subfigure}[b]{0.20 \textwidth}
        \includegraphics[width=\textwidth]{Figures/Figure7/Figure7_c.pdf}
        \caption{AMA RF Response}
        \label{fig:case12FiltersResponse}
    \end{subfigure}    
        \begin{subfigure}[b]{0.2 \textwidth}
        \includegraphics[width=\textwidth]{Figures/Figure7/Figure7_d.pdf}
        \caption{Luminance Estimates}
        \label{fig:case12Results}
    \end{subfigure}
    \label{fig:case12AllResults}
    \caption{{\bf Receptive fields and lightness estimates. Case 3:}  Same as Fig. \ref{fig:case9AllResults}.}
\end{figure}

% Figure 8
\begin{figure}
\centering
\begin{subfigure}[b]{0.3 \textwidth}
	\includegraphics[width=\textwidth]{Figures/Figure8/Figure8_a.pdf}
	\caption{Performance of methods}
	\label{fig:summaryBarGraph}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.3 \textwidth}   
	\includegraphics[width=\textwidth]{Figures/Figure8/Figure8_b.pdf}
	\caption{SVD RF Performance}
	\label{fig:SVDBAR}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.3 \textwidth}
	\includegraphics[width=\textwidth]{Figures/Figure8/Figure8_c.pdf}
	\caption{AMA RF Performance}
	\label{fig:AMABAR}
    \end{subfigure}
\caption{{\bf Model and Filter Performance:} (a) Comparison of various methods on lightness estimations for the three cases studied here. For simple spectral variations, like where only the target reflectance varies (case 1) or only the target and illumination spectrum varies (Case 2), the lightness can be estimated well. This is so, because the lightness information can be estimated simply from the light reflected of the target( case 1) or from the contrast between the target and the {\it fixed} background (case 2). For more complex case, where the lightness information is confounded due to variations in target, background and illuminant (case 3), the estimation has higher variability. (b) Performance of the SVD receptive fields obtained from one case on the stimuli of others. The RFs obtained from any one of the three cases perform well on the stimuli from case 1. The RF of the most complicated case (case 3), has good performance on the stimuli of lower complexity. (c) Same as Fig.\ref{fig:SVDBAR} for AMA RFs.}
 \label{fig:barGraphs}
\end{figure}

@@

% Figure 9
\begin{figure}[t]
\centering
\begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{Figures/Figure9/Figure9_a.png}
        \caption{Library }
        \label{fig:baseSceneLibrary}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{Figures/Figure9/Figure9_b.png}
        \caption{Mill}
        \label{fig:baseSceneMill}
    \end{subfigure}    
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{Figures/Figure9/Figure9_c.png}
        \caption{Table-Chairs}
        \label{fig:baseSceneTableChairs}
    \end{subfigure}

    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{Figures/Figure9/Figure9_d.png}
        \caption{Indoor-plant}
        \label{fig:baseSceneIndoorPlant}
    \end{subfigure}    
    ~
    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{Figures/Figure9/Figure9_e.png}
        \caption{Warehouse}
        \label{fig:baseSceneWarehouse}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{Figures/Figure9/Figure9_f.png}
        \caption{Checkerboard}
        \label{fig:baseSceneCheckerBoard}
    \end{subfigure}
    \caption{Example of base scenes.}\label{fig:baseScenes}
\end{figure}

@@

% Figure 10
\begin{figure}[h]
\centering
\begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{Figures/Figure10/Figure10_a.png}
        \caption{Big-ball}
        \label{fig:libraryWithBigBall}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
\begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{Figures/Figure10/Figure10_b.png}
        \caption{Small-ball}
        \label{fig:libraryWithSmallBall}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{Figures/Figure10/Figure10_c.png}
        \caption{Barrel}
        \label{fig:libraryWithBarrel}
    \end{subfigure}

>>>>

In this work, we study a simpler analogue of color constancy called lightness constancy. Of the 3D human perceptual color space, we only consider the lightness component. Lightness is the attribute that determines the brightness of a color. A color with a low lightness is nearly black, while one with a high lightness is the pure, saturated color. For achromatic objects, it is the property that changes from black to gray to white. We study the effects of variations in the reflected light on the perceived lightness of an object.

% Figure 1: Introduction
\begin{figure}[h]
\centering
\begin{subfigure}{0.4 \textwidth}
		\centering
        \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_a.png}
        \caption{}
        \label{fig:introSchematic}
    \end{subfigure}
    \begin{subfigure}{0.45 \textwidth}   
        \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_b.jpeg}
        \caption{}
        \label{fig:introExampleFigure}
    \end{subfigure}
    \label{introFigure}
    \caption{(a) {\bf Color Constancy:} The light reflected off an object and incident on our eyes, depends both on the surface reflectance of the object $\left( R(\lambda,x) \right)$ and the illumination spectrum of the light source $\left(E(\lambda,x)\right)$. Additionally, the reflected light also depends on context the object lies in. Thus a variation in the reflected light can result from either a change in the object surface reflectance, or a change in the illumination spectrum of the light source, or change in the context, or all of these. Color constancy refers to the ability of the human visual system to perceive the color of the object stably under variations coming from these factors. (b) {\bf Lightness Constancy Under Spectral Variations:} In this work we study lightness constancy under variations in the spectra of the light sources and the objects. In Fig.\ref{fig:introExampleFigure}, we show 5 images generated at three different lightness levels of the target object (spherical object in the center). Along the rows we have fixed the lightness level of the target object, while we vary the spectra of the target object, the background objects and the light sources. (For illustration, in fig.\ref{fig:introExampleFigure}, We have fixed the shape of the target object reflectance spectra along the column.) Our aim is to identify computations that can recover the target object lightness from such stimuli.} 
\end{figure}

The variations in the reflected light can result from either geometrical factors (like shape, size, relative position of objects, etc.) or spectral factors (such as the illumination spectra, surface reflectance, diffusivity, etc.). In this work, we focus on the spectral factors. Specifically, we study the effects of variations in the surface reflectance spectra and the illumination spectra on lightness perception. We are interested in identifying the computations that can lead to stable lightness perception and constancy (Fig.\ref{fig:introExampleFigure}).

@@

We employ a supervised learning approach to understand this phenomenon. Our approach involves generating a database of multi-spectral images of naturalistic scenes. These images are labeled by the lightness of a specific target object in the scene. The image label depends on the reflectance of the target object. It refers to the perceived lightness of the target object if it were placed under a standard light source ($D_{65}$ daylight spectrum). We generate hundreds of multi-spectral images at several fixed values of the target object standard lightness. At a particular lightness level, we allow variations in the surface reflectance spectra of the objects (both the target and the surround objects) and the illumination spectra of the light sources (Fig. \ref{fig:introExampleFigure}.

In this work, we study three cases resulting from the combination of such spectral variations (Fig.\ref{fig:studiedCases}. These cases are: 1. Variations in target object spectra (Fig.\ref{fig:targetVarying}) with fixed illumination and background surface reflectance spectra, 2. Variations in target object spectra and the light source spectra, with fixed background surface reflectance spectra (Fig.\ref{fig:targetIlluminantVarying}), and 3. Variations in all spectra (target object, background object and light source) (Fig.\ref{fig:allSpectraVarying}). The effects of other types of spectral variations can be explained in terms of one of these cases (see supplementary information).

% Figure 2: Cases Studied
\begin{figure}
\centering
	\begin{subfigure}[b]{0.33 \textwidth}
		\includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_a.jpeg}
		\caption{Case 1}
 		\label{fig:targetVarying}
	\end{subfigure}
	\begin{subfigure}[b]{0.33 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_b.jpeg}
        \caption{Case 2}
        \label{fig:targetIlluminantVarying}
    \end{subfigure}
	\begin{subfigure}[b]{0.33 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_c.jpeg}
        \caption{Case 3}
        \label{fig:allSpectraVarying}
    \end{subfigure}    
    \caption{{\bf Three types of spectral variations studied in this work:} sRGB rendition of images studied in our work. The numbers on the left are the standard lightness level of the target object. We show 5 images for each case at 3 lightness levels. The analysis was performed with images at 10 lightness levels. We studied three types of spectral variations. (a) Case 1: Target reflectance spectra variable, Background reflectance spectra fixed, illuminant spectra fixed (b) Case 2: Target reflectance spectra variable, Background reflectance spectra fixed, illuminant spectra variable (c) Case 3: Target reflectance spectra variable, Background reflectance spectra variable, illuminant spectra variable.}
\label{fig:studiedCases}
\end{figure}

Having generated the database of labeled multi-spectral images for each one of these cases, we simulate the retinal cone response to these images using an accurate model of the eye. These cone-responses datasets, that are labeled with the standard lightness of the target object, are analyzed using supervised computational learning methods. We have employed three supervised computational learning methods for estimating the target object lightness: linear regression, a generalized SVD regression and accuracy maximization analysis. These methods identify the computations that need to be performed on the cone-responses to estimate the target object lightness. Finally, we evaluate the performance of the computational methods on a test set of images.

In the following, we describe each one of these stages of our approach in detail. In the methods section, we first describe the process to generate naturalistic labeled images (\nameref{method:VirtualWorld}). Next, we describe the steps to simulate the response of the retinal cones to these images (\nameref{method:Isetbio}). Finally, we describe the three learning methods we have used in our analysis (\nameref{method:SupervisedLearning}). In the results section, we show the estimates and performance of each one of the supervised methods for the three cases with different spectral variations.

We show that for spectral variations that allow variation either only in the target surface reflectance or the background surface reflectance or the spectral power distribution of the source of light, the standard lightness, $Y_{65}$ can be recovered by simple manipulations of the reflected light captured by the visual system. For example, if the illumination spectra of the light sources and the background are held fixed, while the target reflectance spectra change (case 1), $Y_{65}$ can be recovered directly from the light reflected off the target object. If the surface reflectance of the target object and the illumination spectra of the light sources are allowed to vary, but the background reflectance spectra is fixed (case 2), $Y_{65}$ can be recovered by from the contrast between the target and the background. When all the spectral features in the scene are allowed to change (case 3), $Y_{65}$ can not be recovered from a simple manipulations of the light captured by the visual system. Here, we have used a Bayesian supervised learning method called accuracy maximization analysis to estimate $Y_{65}$ of the target object. Using this method, we can recover the lightness of the target object with $\sim 15\%$ relative root mean square error.

@@

% Figure 3: Methods
\begin{figure}
\centering
\begin{subfigure}[b]{0.25 \textwidth}
		\centering
        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_a.png}
        \caption{A typical 3D Scene}
        \label{fig:3DScene}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.19 \textwidth}   
    \hspace{0.1 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_b.png}
        \caption{Cropped Image}
        \label{fig:croppedImage}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.19 \textwidth}
    \hspace{0.1 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_c.png}
        \caption{Optical Image}
        \label{fig:croppedImageWithMosaic}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.2 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_d.png}
        \caption{LMS cone contrast}
        \label{fig:coneContrast}
    \end{subfigure}

@@

% Figure 4
\begin{figure}
\centering
\begin{subfigure}[b]{0.27 \textwidth}
		\centering
        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_a.pdf}
        \caption{SVD First 2 RFs}
        \label{fig:case9SVD}
    \end{subfigure}
    \begin{subfigure}[b]{0.27 \textwidth}   
        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_b.pdf}
        \caption{AMA First 2 RFs}
        \label{fig:case9AMA}
    \end{subfigure}
        \begin{subfigure}[b]{0.20 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_c.pdf}
        \caption{AMA RF Response}
        \label{fig:case9FiltersResponse}
    \end{subfigure}
        \begin{subfigure}[b]{0.20 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_d.pdf}
        \caption{Lightness Estimates}
        \label{fig:case9Results}
    \end{subfigure}    
    \caption{{\bf Receptive fields and lightness estimates. Case 1:} (a) First two receptive fields produced by the SVD method. Along the row we show the filters corresponding to the L cones, M cones and Scones (left to right). (c) First two receptive fields produced by the SVD method. (c) The response of the stimuli to the first two AMA filters. The responses are grouped with the label of the stimuli. As is clear, the response separate out quite well in this case, making the estimation easy (d) The estimates of the target object standard lightness. The naive method produces the mean value of the target luminance used in the analysis. The shaded region corresponds to 1 sigma standard deviation.}
\label{fig:case9AllResults}
\end{figure}

% Figure 5
\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{../Figures/Figure5/Figure5.pdf}
\caption{{\bf Performance with number of RFs used for estimation:} Most of the information is captured by the first two filters. We have used the first 8 RFs in our analysis.}
\label{fig:RMSEvsNFilters}
\end{figure}

% Figure 6
\begin{figure}
\centering
\begin{subfigure}[b]{0.27 \textwidth}
		\centering
        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_a.pdf}
        \caption{SVD First 2 RFs}
        \label{fig:case10SVD}
    \end{subfigure}
    \begin{subfigure}[b]{0.27 \textwidth}   
        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_b.pdf}
        \caption{AMA First 2 RFs}
        \label{fig:case10AMA}
    \end{subfigure}
        \begin{subfigure}[b]{0.20 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_c.pdf}
        \caption{AMA RF Response}
        \label{fig:case10FiltersResponse}
    \end{subfigure}    
        \begin{subfigure}[b]{0.2 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_d.pdf}
        \caption{Luminance Estimates}
        \label{fig:case10Results}
    \end{subfigure}
    \label{fig:case10AllResults}
    \caption{{\bf Receptive fields and lightness estimates. Case 2:} Same as Fig. \ref{fig:case9AllResults}.}
\end{figure}

% Figure 7
\begin{figure}
\centering
\begin{subfigure}[b]{0.27 \textwidth}
		\centering
        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_a.pdf}
        \caption{SVD First 2 RFs}
        \label{fig:case12SVD}
    \end{subfigure}
    \begin{subfigure}[b]{0.27 \textwidth}   
        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_b.pdf}
        \caption{AMA First 2 RFs}
        \label{fig:case12AMA}
    \end{subfigure}
        \begin{subfigure}[b]{0.20 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_c.pdf}
        \caption{AMA RF Response}
        \label{fig:case12FiltersResponse}
    \end{subfigure}    
        \begin{subfigure}[b]{0.2 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_d.pdf}
        \caption{Luminance Estimates}
        \label{fig:case12Results}
    \end{subfigure}
    \label{fig:case12AllResults}
    \caption{{\bf Receptive fields and lightness estimates. Case 3:}  Same as Fig. \ref{fig:case9AllResults}.}
\end{figure}

% Figure 8
\begin{figure}
\centering
\begin{subfigure}[b]{0.3 \textwidth}
	\includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_a.pdf}
	\caption{Performance of methods}
	\label{fig:summaryBarGraph}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.3 \textwidth}   
	\includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_b.pdf}
	\caption{SVD RF Performance}
	\label{fig:SVDBAR}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.3 \textwidth}
	\includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_c.pdf}
	\caption{AMA RF Performance}
	\label{fig:AMABAR}
    \end{subfigure}
\caption{{\bf Model and Filter Performance:} (a) Comparison of various methods on lightness estimations for the three cases studied here. For simple spectral variations, like where only the target reflectance varies (case 1) or only the target and illumination spectrum varies (Case 2), the lightness can be estimated well. This is so, because the lightness information can be estimated simply from the light reflected of the target( case 1) or from the contrast between the target and the {\it fixed} background (case 2). For more complex case, where the lightness information is confounded due to variations in target, background and illuminant (case 3), the estimation has higher variability. (b) Performance of the SVD receptive fields obtained from one case on the stimuli of others. The RFs obtained from any one of the three cases perform well on the stimuli from case 1. The RF of the most complicated case (case 3), has good performance on the stimuli of lower complexity. (c) Same as Fig.\ref{fig:SVDBAR} for AMA RFs.}
 \label{fig:barGraphs}
\end{figure}

@@

% Figure 9
\begin{figure}[t]
\centering
\begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_a.png}
        \caption{Library }
        \label{fig:baseSceneLibrary}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_b.png}
        \caption{Mill}
        \label{fig:baseSceneMill}
    \end{subfigure}    
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.png}
        \caption{Table-Chairs}
        \label{fig:baseSceneTableChairs}
    \end{subfigure}

    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_d.png}
        \caption{Indoor-plant}
        \label{fig:baseSceneIndoorPlant}
    \end{subfigure}    
    ~
    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_e.png}
        \caption{Warehouse}
        \label{fig:baseSceneWarehouse}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_f.png}
        \caption{Checkerboard}
        \label{fig:baseSceneCheckerBoard}
    \end{subfigure}
    \caption{Example of base scenes.}\label{fig:baseScenes}
\end{figure}

@@

% Figure 10
\begin{figure}[h]
\centering
\begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_a.png}
        \caption{Big-ball}
        \label{fig:libraryWithBigBall}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
\begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_b.png}
        \caption{Small-ball}
        \label{fig:libraryWithSmallBall}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_c.png}
        \caption{Barrel}
        \label{fig:libraryWithBarrel}
    \end{subfigure}

    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_d.png}
        \caption{Xylophone}
        \label{fig:libraryWithXylophone}
    \end{subfigure}
    ~
	\begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_e.png}
        \caption{Ring toy}
        \label{fig:libraryWithRingToy}
    \end{subfigure}
        ~
    	\begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_f.png}
        \caption{Champagne Bottle}
        \label{fig:libraryWithChampagneBottle}
    \end{subfigure}
\caption{Base scenes with inserted objects.}\label{fig:libraryWithTarget}
\end{figure}
